Analyzing Toronto Island Ferry Ticket Counts

### 2024-09-26 outputs/paper/paper.qmd
Deleted unneeded code that writes to the csv files

raw_data_path <- "C:/Users/yuqiu/ferrySale/ferrySale-main/inputs/data/raw_data.csv"
cleaned_data_path <- "C:/Users/yuqiu/ferrySale/ferrySale-main/outputs/data/cleaned_data.csv"

write_csv(marriage_licence_statistics, raw_data_path)

raw_data <- read_csv(raw_data_path, show_col_types = FALSE)

cleaned_data <- raw_data
write_csv(cleaned_data, cleaned_data_path)
data <- read_csv(cleaned_data_path, show_col_types = FALSE)

@@

# Load the cleaned data from the CSV file (adjust the path as needed)
data <- read_csv("C:/Users/yuqiu/ferrySale/ferrySale-main/outputs/data/cleaned_data.csv", show_col_types = FALSE)

>>>>

# Read the cleaned data
data <- read_csv(file = here("outputs/data/cleaned_data.csv"), 
                 show_col_types = FALSE)

@@

# Load the cleaned data from the CSV file (adjust the path as needed)
data <- read_csv(file = here("outputs/data/cleaned_data.csv"), show_col_types = FALSE)
